Sampling requirements to detect ecosystem change

### 2020-02-18 R/manuscript_draft.Rmd
edit on fig size

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 7.2, fig.height= 3,fig.cap='Distance to real changepoint per total number of samples analyzed, following (a) random sampling, (b) regular sampling, and (c) iterative sampling. Total number of samples was set between 5 and 30, out of the 74 initial time series.  \\label{fig:case_study_number_sample}'}
library(ggplot2)
#devtools::install_github("rensa/stickylabeller")
library(stickylabeller)
p1 <- ggplot(myoutput[myoutput$target_cpt==1,], aes(final_n,diff_real, pch=factor(n2_init))) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method,
             labeller = label_glue('({.l}) {method} sampling ')) + 
  theme_bw() +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") +
  theme(legend.position = c(0.93, 0.75),
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title=element_text(size=7), 
        legend.text=element_text(size=8)) +
  guides(pch=guide_legend(title="Initial number\nof sample"))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 4, fig.height= 6.5, fig.cap='Iterative sampling and impact on ordination. (a) Full time series, on which "true" changepoint was detected. (b) First step of iterative sampling, n = 5. (c) Final step of iterative samples: by adding 4 samples, the true changepoint was detected. \\label{fig:case_study_iterative_sampling}'}

@@

# Plot with all data
 p_init <- ggplot(vrall$matrix, aes(age, x)) + geom_point(alpha = .3) + geom_line(alpha = .3) +
  theme_bw()  +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
           geom_rect(mapping=aes(xmin=vrall$matrix$age[which(vrall$matrix$index==vrall$changepoint)-1], xmax=vrall$matrix$age[which(vrall$matrix$index==vrall$changepoint)], ymin=0, ymax=2), alpha=0.008, fill="grey") +
   labs(subtitle = paste0("a. Full time-series, n = ", nrow(vr)), x="Year", y="DCA first component",
        color='samples added\nat iteration t=') +
   geom_point(vr_out_order, mapping=aes(age, x, color = as.factor(count)), cex=2) +
   geom_text(vr_out_order, mapping=aes(age, x, label =count), vjust = 1.5, nudge_x = 1.5) +
   scale_color_manual(values=mypal)

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 7.2, fig.height= 3,fig.cap='Distance to real changepoint per total number of samples analyzed, following (a) random sampling, (b) regular sampling, and (c) iterative sampling. Total number of samples was set between 5 and 30, out of the 74 initial time series.  \\label{fig:case_study_number_sample}'}
library(ggplot2)
#devtools::install_github("rensa/stickylabeller")
library(stickylabeller)
p1 <- ggplot(myoutput[myoutput$target_cpt==1,], aes(final_n,diff_real, pch=factor(n2_init))) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method,
             labeller = label_glue('({.l}) {method} sampling ')) + 
  theme_bw() +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") +
  theme(legend.position = c(0.93, 0.72),
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title=element_text(size=7), 
        legend.text=element_text(size=8)) +
  guides(pch=guide_legend(title="Initial number\nof sample"))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 5, fig.height= 7, fig.cap='Iterative sampling and impact on ordination. (a) Full time series, on which "true" changepoint was detected. (b) First step of iterative sampling, n = 5. (c) Final step of iterative samples: by adding 4 samples, the true changepoint was detected. \\label{fig:case_study_iterative_sampling}'}

@@

# Plot with all data
 p_init <- ggplot(vrall$matrix, aes(age, x)) + geom_point(alpha = .3) + geom_line(alpha = .3) +
  theme_bw()  +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
           geom_rect(mapping=aes(xmin=vrall$matrix$age[which(vrall$matrix$index==vrall$changepoint)-1], xmax=vrall$matrix$age[which(vrall$matrix$index==vrall$changepoint)], ymin=-1, ymax=2), alpha=0.05, fill="grey") +
   labs(subtitle = paste0("a. Full time-series, n = ", nrow(vr)), x="Year", y="DCA first component",
        color='samples added\nat iteration t=') +
   geom_point(vr_out_order, mapping=aes(age, x, color = as.factor(count)), cex=2) +
   geom_text(vr_out_order, mapping=aes(age, x, label =count), vjust = 1.5, nudge_x = 1.5) +
   scale_color_manual(values=mypal)
